Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
added comment

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
embedded control software. It is based on the principle of describing a physical system
as an equivalent finite-state machine and computing reachability over the finite-state 
machine. Pessoa can synthesise safe embedded controller software for a range of properties based on a safety specification over state
values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
synthesising a fixed point digital controller.

@@

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
with full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. 
Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.

>>>>

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
embedded control software. It is based on the principle of describing a physical system
as an equivalent finite-state machine and computing reachability over the finite-state 
machine. Pessoa can synthesise safe embedded controller software for a range of properties based on a safety specification over state
values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
synthesising a fixed-point digital controller.

@@

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
with full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into \textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. 
Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.
